\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and a Multi-Armed Bandit Model with Correlated Rewards to Accelerate Robust Grasp Planning \versionline{9}

### 2015-09-15 ICRA2016/bandits_docs/includes/abstract.tex
First 8 page version ready with fb from Mel and Mathieu as well

\begin{abstract}
Recent advances in distributed computing and machine learning combined with very large datasets of images and human speech have produced a series of results that surpass decades of research in analytic methods and, in some cases, human ability.
This raises the question: can Big Data and Cloud computation produce analogous advances in robot grasping and manipulation?
We develop a Multi-Armed Bandit algorithm with correlated rewards and show that our algorithm can leverage a large dataset of prior grasps and 3D object models to reduce the number of samples needed for robust grasp planning.
To study scaling effects, we introduce the Dexterity Network (Dex-Net) 1.0, a growing dataset that currently includes over 10,000 unique 3D object models and 2.5 million parallel-jaw grasps along with the probability of force closure of each under uncertainty in object pose, gripper pose, and friction coefficient.
We use multi-view Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, to learn a similarity metric between objects and apply MV-CNNs to indexing similar objects for grasp planning at scale.
We implement Dex-Net 1.0 using the Google Cloud Platform with a system that can run up to 1,500 virtual machines at a time, reducing experiment runtime by up to 1000$\times$.
Experiments suggest that robust grasp planning is up to $3.5\times$ faster than Thompson sampling without prior data on average and that average grasp quality scales with the size of the dataset when the MV-CNN returns geometrically similar objects.%, and that the convergence rate can descrease if the similarity metric measures false correlations between grasps.
We also explore sensitivity of our algorithm to similarity metrics and pose and friction uncertainty levels for test objects.
Code, data, and additional information can be found at: \TODO{Url}
\end{abstract}

>>>>

\begin{abstract}
Advances in computing and massive datasets of images and human speech have produced recent results that surpass decades of past research on analytic methods..
This raises the question: can Big Data and Cloud Computation produce analogous advances in robot grasping and manipulation?
We develop an algorithm based on a Multi-Armed Bandit model with correlated rewards and show that our algorithm can leverage a large dataset of prior grasps and 3D object models to reduce the number of samples needed for robust grasp planning.
To study scaling effects, we introduce the Dexterity Network (Dex-Net) 1.0, a growing dataset that currently includes over 10,000 unique 3D object models and 2.5 million parallel-jaw grasps along with the probability of force closure of each grasp under uncertainty in object pose, gripper pose, and friction coefficient.
We use Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, to learn a similarity metric between objects and apply MV-CNNs to indexing similar objects for grasp planning at scale.
We implement Dex-Net 1.0 using the Google Cloud Platform with a system that can simultaneously run up to 1,500 virtual machines, reducing experiment runtime by up to 1000$\times$.
Experiments suggest that robust grasp planning is up to 3.5$\times$ faster than Thompson sampling without prior data and that average grasp quality scales with the size of the dataset when the MV-CNN returns geometrically similar objects.
We also explore sensitivity of our algorithm to similarity metrics and pose and friction uncertainty levels for test objects.
Code, data, and additional information can be found at: \TODO{Url}
\end{abstract}

### 2015-09-15 ICRA2016/bandits_docs/includes/algorithm.tex
First 8 page version ready with fb from Mel and Mathieu as well

\section{Correlated Multi-Armed Bandit Algorithm}
\seclabel{algorithm}
Our algorithm (see Algorithm~\ref{alg:full}) optimizes $P_F$ over a set of candidate grasps on a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards~\cite{hoffman2013exploiting, pandey2007multi} and priors computed from Dex-Net 1.0.
We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior distribution for each grasp using the Dex-Net database $\mD$.
Next, we run MAB by selecting a grasp using Thompson sampling~\cite{laskey2015bandits, oberlin2015autonomously}, sampling from our uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the $P_F$ for each grasp.
Finally, we return the grasp for which the belief distribution has the maximum lower confidence bound, a conservative estimate of the grasp with the highest estimated $P_F$.
We acknowledge that many alternatives for grasp sampling exist~\cite{kroemer2010combining, montesano2012active, oberlin2015autonomously}, however in this work we are interested in studying the scaling effects for a fixed selection method.

@@

\subsection{Belief Distribution Model}
\seclabel{belief}
Let $\mO$ denote the input object to Algorithm~\ref{alg:full}, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ from samples of object pose, gripper pose, and friction as described in \secref{quality}.
Under our model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
Since $\theta_j$ is unknown, our algorithm maintains a posterior belief distribution for each $\theta_j$ based on the outcome of past force closure evaluations.
Our belief distribution on the Bernoulli parameter $\theta_{j}$ is a Beta distribution~\cite{hoffman2013exploiting, laskey2015bandits}, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

\vspace{-2ex}
\begin{align*}
	\betadist(\alpha, \beta) = \frac{1}{B(\alpha, \beta)} \theta_j^{\alpha-1} (1 - \theta_j)^{\beta-1}
\end{align*}
\noindent Our Bayesian MAB algorithms updates this belief for every new force closure evaluation, converging toward a delta distribution on the true $P_F$.

@@

We measure similarity using a set of feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., 3$, where $d_m$ is the dimension of the feature space for each.
Our first feature map $\phi_{1}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ captures similiarity in the grasp parameters, where $\bx \in \bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
To capture local surface geometry, our second feature map $\phi_{2} = \eta$, where $\eta$ is the differential heightmap described in \secref{grasp-similarity}.
To capture global shape information, our third feature map $\phi_{3}(\mY) = \psi(\mO)$, where $\psi$ is our object similiary map described in \secref{object-similarity}.
Given the feature maps, we use the squared exponential kernel 
\begin{align*}
	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{3} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{C_m}^2 \right).
\end{align*}
\noindent where $C_m \in \bR^{d_m \times d_m}$ is the bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T (C_m^T C_m)^{-1} \by$.
The bandwidths are hyperparameters of the algorithm that are be set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_F$ for grasps under the model on a set of training data~\cite{rasmussen2006}.

>>>>

\section{Correlated Multi-Armed Bandit Algorithm}
\seclabel{algorithm}
The Dex-Net 1.0 algorithm (see below) optimizes $P_F$ over a set of candidate grasps on a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards~\cite{hoffman2013exploiting, pandey2007multi} and priors computed from Dex-Net 1.0.
We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior distribution for each grasp using the Dex-Net database $\mD$.
Next, we run MAB by selecting a grasp using Thompson sampling~\cite{laskey2015bandits, oberlin2015autonomously}, sampling from our uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the $P_F$ for each grasp.
Finally, we return the grasp for which the belief distribution has the maximum lower confidence bound, a conservative estimate of the grasp with the highest estimated $P_F$.
We acknowledge alternatives for grasp selection on each iteration~\cite{kroemer2010combining, laskey2015bandits, montesano2012active, oberlin2015autonomously}, but use Thompson sampling to study the scaling effects for a fixed selection method.

@@

\subsection{Belief Distribution Model}
\seclabel{belief}
Let $\mO$ denote the test object to label with the Dex-Net Algorithm, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
Our Bayesian MAB algorithm works by maintaining a belief on the $P_F$ for each grasp that is updated with every new force closure evaluation, assigning increasingly high probability to the true $P_F$. 
We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ from samples of object pose, gripper pose, and friction as described in \secref{quality}.
Under our model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
Since $\theta_j$ is unknown, our algorithm maintains a posterior belief distribution on the Bernoulli parameter $\theta_{j}$ using a Beta distribution~\cite{hoffman2013exploiting, laskey2015bandits}, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

\vspace{-4ex}
\begin{align*}
	\betadist(\alpha, \beta) = \left( 1 / B(\alpha, \beta) \right) \theta_j^{\alpha-1} (1 - \theta_j)^{\beta-1}
\end{align*}
\noindent where $B$ is a normalization constant.

@@

We measure similarity using a set of feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., 3$, where $d_m$ is the dimension of the feature space for each.
Our first feature map $\phi_{1}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ captures similiarity in the grasp parameters, where $\bx \in \bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
To capture local surface geometry, our second feature map $\phi_{2} = \eta$, where $\eta$ is the differential heightmap described in \secref{grasp-similarity}.
To capture global shape information, our third feature map $\phi_{3}(\mY) = \psi(\mO)$, where $\psi$ is our object similiary map described in \secref{object-similarity}.
Given the feature maps, we use the squared exponential kernel 
\begin{align*}
	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{3} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{C_m}^2 \right).
\end{align*}
\noindent where $C_m \in \bR^{d_m \times d_m}$ is the bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T (C_m^T C_m)^{-1} \by$.
The bandwidths are hyperparameters of the algorithm that are set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_F$ under the CCBP on a set of training data.

### 2015-09-15 ICRA2016/bandits_docs/includes/conclusion.tex
First 8 page version ready with fb from Mel and Mathieu as well

\section{Discussion and Future Work}
\seclabel{conclusion}
We developed the Dex-Net 1.0 algorithm using a Multi-Armed Bandit model withcorrelated rewards to reduce the number of samples required to plan robust parallel-jaw grasps by leveraging prior grasps and 3D object models.
To study scaling effects, we introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 3D object models and 2.5 million parallel-jaw grasps, and MV-CNNs~\cite{su2015multi} to efficiently index similar objects.
%For efficient indexing of similar objects in Dex-Net, we used multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art deep learning method of object classification.
Our experiments suggest that increasing the amount of prior knowledge of objects and the quality of grasps on each object enables up to a $10\times$ speedup in the time to compute a grasp with high probability of force closure for a new object, and also suggest that convergence is fastest when the object has a set of geometrically similar nearest neighbors in the database.

One current shortcoming of our method is that it relies on a set of features manually designed to predict grasp quality for a grasp and object, such as heightmaps and CNNs that predict object category.
Future work will leverage recent developments in feature learning with Deep Neural Networks~\cite{krizhevsky2012imagenet} to optimize grasp and object representations directly based on the outcome of grasp evaluations from bandit algorithms.
We are also interested in a pipelined approach that integrates research on deep learning to maps directly from images to motor torques that control a grasp.
To do so, we will use supervision from the data in Dex-Net to study prediction of object identity and pose directly from depth images~\cite{aubry2015understanding, guptaCVPR15a} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}. 
%We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface and to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies, with the goal of a future system that maps directly from images to motor torques.

In future work, we will also add grasp and object data to Dex-Net, such as more 3D models, task constraints, the outcomes of physical trials, or human annotations.
%This presents a challenge because the number of labels per object and grasp may be smaller that with probability of force closure due to the time cost involved.
%Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
We will also explore additional analytic grasp metrics to Dex-Net such as cages~\cite{diankov2010automated}, different grasp selection policies such as Gittins indices, and extensions to plan a set of grasps that ``cover" an object surface to increase the chances that a grasp is reachable in cluttered environments.
We will also include uncertainty in object shape resulting from noisy point clouds~\cite{mahler2015gp} to future models.
Our goal is to release Dex-Net in the future as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.

>>>>

\section{Discussion and Future Work}
\seclabel{conclusion}
We developed the Dex-Net 1.0 algorithm using a Multi-Armed Bandit model with correlated rewards to reduce the number of samples required to plan robust parallel-jaw grasps by leveraging prior grasps and 3D object models.
To study scaling effects, we introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 3D object models and 2.5 million parallel-jaw grasps, and MV-CNNs~\cite{aubry2015understanding, su2015multi} to efficiently index similar objects.
%For efficient indexing of similar objects in Dex-Net, we used multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art deep learning method of object classification.
Our experiments suggest that increasing the amount of prior knowledge of objects and the quality of grasps on each object enables up to a $10\times$ speedup in the time to compute a grasp with high probability of force closure for a new object, and also suggest that convergence is fastest when the object has a set of geometrically similar nearest neighbors in the database.

One current shortcoming of our method is that it relies on a set of features manually designed to predict grasp quality for a grasp and object, such as heightmaps and CNNs that predict object category.
Future work will leverage recent developments in feature learning with Deep Neural Networks~\cite{krizhevsky2012imagenet} to optimize grasp and object representations directly based on the outcome of grasp evaluations from bandit algorithms.
We are also interested in an end-to-end approach that integrates research on deep learning to map directly from images to motor torques that control a grasp.
To do so, we will use supervision from the data in Dex-Net to study prediction of object identity and pose directly from depth images~\cite{aubry2015understanding} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}. 
%We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface and to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies, with the goal of a future system that maps directly from images to motor torques.

In future work, we will also add grasp and object data to Dex-Net, such as more 3D models, task constraints, the outcomes of physical trials, or human annotations.
%This presents a challenge because the number of labels per object and grasp may be smaller that with probability of force closure due to the time cost involved.
%Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
We will also explore additional analytic grasp metrics to Dex-Net such as cages, different grasp selection policies such as Gittins indices, and extensions to plan a set of grasps that ``cover" an object surface to increase the chances that a grasp is reachable in cluttered environments.
We will also include uncertainty in object shape resulting from noisy point clouds~\cite{mahler2015gp} to future models.
Our goal is to release Dex-Net in the future as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.
